---
title: "Presentation1"
author: "Me"
date: "1/22/2018"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Double hash means new slide; text following it is title
### Three hashes means top-level subheading
#### Four hashes means second-level subheading
Some content

***
Three asterisks means a slide without a title

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with ordered list

1. Item a
2. Item b

## Slide with some formatting stuff

Plain text 

*italicization*

**bold**

Code signalled by single right-facing quotes (the thing on the upper left of the keyboard; forget name)
`for (i %in% 1 : 10)`

## Slide with code to actually run

Triple little thingies at beginning and end.  Start ones are followed by {r} to signal R code.
```{r, comment = '', echo = TRUE, eval = FALSE}
head(mtcars)
```

## Slide with plot

```{r, fig.align='center', fig.cap='Caption'}
plot(mtcars$wt, mtcars$mpg, xlab='Weight', ylab='MPG')
```


